---
output: 
    stevetemplates::statement:
    latex_engine: pdflatex
geometry: margin=1in

title: "Dr. Hayashi Project"
author: Akihiro Shiroshita
affiliation: Department of Respiratory Medicine, Ichinomiyanishi Hospital
email: "akihirokun8@gmail.com"

fontfamily: cochineal
fontsize: 11pt
---

# Setting-up  

```{r echo=TRUE, message=FALSE, warning=FALSE}
packages = c("devtools",
             "usethis",
             "here",
             "readr",
             "data.table",
             "readxl",
             "tidyverse",
             "tidylog",
             "lubridate",
             "ggplot2",
             "ggthemes",
             "rlang",
             "metafor",
             "metaforest",
             "clubSandwich",
             "netmeta",
             "dmetar",
             "rgl",
             "gemtc",
             "igraph",
             "dmetar")
package.check <- lapply(packages, FUN = function(x){
  if (!require(x, character.only = TRUE)){
    install.packages(x, dependencies = TRUE)
    library(x, character.only = TRUE)
  }
})

immediate_success <- read_csv(here("input", "immediate_success_rate.csv"), 
    locale = locale(encoding = "SHIFT-JIS"))
#length_of_hospital_stay <- read_csv(here("input", "length_of_stay.csv"), 
#    locale = locale(encoding = "SHIFT-JIS"))
#patient_satisfaction <- read_csv(here("input","patient_satisfaction.csv"), 
#    locale = locale(encoding = "SHIFT-JIS"))
pain_score <- read_csv(here("input", "pain_score.csv"),
                       locale = locale(encoding = "SHIFT-JIS"))
```

# Pain score  

```{r}
pain_score
```

## Calculating standardized mean difference    

```{r}
com <- metacont(ne[1], me[1], se[1],
         nc[1], mc[1], sc[1],
         data = pain_score,
         sm = "SMD")
com$TE
com$seTE
```
## Loop for calculation  

```{r}
pain_score <- pain_score %>% 
  mutate(treat_id = row_number())

# TE

pain_score <- pain_score %>% 
  mutate(TE = map_dbl(1:length(treat_id), ~{
  com <- metacont(ne[[.]], me[[.]], se[[.]], nc[[.]], mc[[.]], sc[[.]],
                  sm = "SMD")
  TE <- com$TE
  return(TE)
}))

# SE

pain_score <- pain_score %>% 
  mutate(seTE = map_dbl(1:length(treat_id), ~{
  com <- metacont(ne[[.]], me[[.]], se[[.]], nc[[.]], mc[[.]], sc[[.]],
                  sm = "SMD")
  seTE <- com$seTE
  return(seTE)
}))

```
```{r}
pain_score
```
  
## Fitting multilevel model  

```{r}

pain_score_sub <- pain_score %>% 
  slice(-9, -10, -11)
multi <- rma.mv(TE, seTE,
                random = list(~ 1 | treat_id,
                              ~ 1 | id),
                data = pain_score_sub)
multi
```

## Robust standard error  

```{r}
coef_test(multi, vcov = "CR2")
```

## Network meta-analysis  

```{r}
new_row <- pain_score %>% 
  filter(id == 6) %>% 
  summarize_all(funs(mean(., na.rm=TRUE)))
new_row[2] <- "Cheok, 2011"

pain_score_nm <- pain_score %>% 
  slice(-6, -7) %>% 
  rbind(new_row)
nm_pain <- netmeta(TE = TE,
                   seTE = seTE,
                   treat1 = treat1,
                   treat2 = treat2,
                   #studlab = id,
                   data = pain_score_nm,
                   sm = "SMD")
nm_pain
```

## Network graph  

```{r}
netgraph(nm_pain)
```
```{r}
netgraph(nm_pain,
         start = "random",
         iterate = TRUE,
         col = "darkgray",
         cex = 1.5,
         multiarm = FALSE,
         points = TRUE,
         col.points = "blue",
         cex.points = 3)
```


# Immediate success rate  

```{r}
immediate_success
```

## Calculating odds ratio    

```{r}
odds <- metabin(ee[2], ne[2], ec[2], nc[2],
                sm = "OR",
                method = "I",
                data = immediate_success)
odds$TE
odds$seTE
```
## Loop for calculation  

```{r}
immediate_success <- immediate_success %>% 
  mutate(treat_id = row_number())

# TE

immediate_success <- immediate_success %>% 
  mutate(TE_odds = map_dbl(1:length(treat_id), ~{
  odds <- metabin(ee[.], ne[.], ec[.], nc[.],
                sm = "OR",
                method = "I")
  TE_odds <- odds$TE
  return(TE_odds)
}))

# SE

immediate_success <- immediate_success %>% 
  mutate(seTE_odds = map_dbl(1:length(treat_id), ~{
  odds <- metabin(ee[.], ne[.], ec[.], nc[.],
                sm = "OR",
                method = "I",
                data = immediate_success)
  seTE_odds <- odds$seTE
  return(seTE_odds)
}))

```
## calculating risk ratio and risk difference  

```{r}
# TE

immediate_success <- immediate_success %>% 
  mutate(TE_rr = map_dbl(1:length(treat_id), ~{
  rr <- metabin(ee[.], ne[.], ec[.], nc[.],
                sm = "RR",
                method = "I")
  TE_rr <- rr$TE
  return(TE_rr)
}))

# SE

immediate_success <- immediate_success %>% 
  mutate(seTE_rr = map_dbl(1:length(treat_id), ~{
  rr <- metabin(ee[.], ne[.], ec[.], nc[.],
                sm = "RR",
                method = "I",
                data = immediate_success)
  seTE_rr <- rr$seTE
  return(seTE_rr)
}))

# TE

immediate_success <- immediate_success %>% 
  mutate(TE_rd = map_dbl(1:length(treat_id), ~{
  rd <- metabin(ee[.], ne[.], ec[.], nc[.],
                sm = "RD",
                method = "I")
  TE_rd <- rd$TE
  return(TE_rd)
}))

# SE

immediate_success <- immediate_success %>% 
  mutate(seTE_rd = map_dbl(1:length(treat_id), ~{
  rd <- metabin(ee[.], ne[.], ec[.], nc[.],
                sm = "OR",
                method = "I",
                data = immediate_success)
  seTE_rd <- rd$seTE
  return(seTE_rd)
}))

```

## Checking dataset  
```{r}
immediate_success
```

## Network meta-analysis  
### Odds ratio  
```{r}
nm_immediate_success <- netmeta(TE = TE_odds,
                   seTE = seTE_odds,
                   treat1 = treat1,
                   treat2 = treat2,
                   #studlab = id,
                   data = immediate_success,
                   sm = "OR")
nm_immediate_success
```
## Risk ratio  

```{r}
nm_immediate_success <- netmeta(TE = TE_odds,
                   seTE = seTE_odds,
                   treat1 = treat1,
                   treat2 = treat2,
                   #studlab = id,
                   data = immediate_success,
                   sm = "RR")
nm_immediate_success
```

## Risk difference  

```{r}
nm_immediate_success <- netmeta(TE = TE_odds,
                   seTE = seTE_odds,
                   treat1 = treat1,
                   treat2 = treat2,
                   #studlab = id,
                   data = immediate_success,
                   sm = "RD")
nm_immediate_success
```